\documentclass[10pt,a4paper,sans]{moderncv} 
\moderncvstyle{banking} 
\moderncvcolor{blue} 
\usepackage{fontawesome5}
\usepackage[scale=0.75]{geometry}
\usepackage{enumitem}

\AtBeginDocument{
  \hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
    citecolor=blue,
    filecolor=blue,
    menucolor=blue,
    runcolor=blue,
    linkbordercolor=blue,
    pdfborderstyle={/S/U/W 1} % sets underlining
}
}


\name{Dr. Krishna}{Narasimhan}
\phone[mobile]{+49~1741750063}
\email{krishna.nm86@gmail.com}
\renewcommand*{\emailsymbol}{{\small\faEnvelope}}
\social[Linkedin][www.linkedin.com/in/krishna-narasimhan-41a8a214/]{\faLinkedin \hspace{0.1cm} LinkedIn}
%\photo[64pt][0.4pt]{krishna.png}

\begin{document}
\pagestyle{empty}
\makecvtitle

\section{Profile}

Expert in software tooling and model based language engineering with significant experience in academia and industry. My expertise includes managing advanced software projects, international collaboration, graduate and undergraduate-level teaching, and R\&D leadership, particularly in software productivity enhancement tools. Academically, I focus on developer tools, program analysis, domain-specific languages, and AI for software assistance. I have a strong record of leading research teams and integrating AI technologies with traditional software engineering


\section{Employment}
\vspace{1ex}
\cventry{November 2023 -- Present}{Head of technology}{AIQ}{Frankfurt, Germany}{}{
  I lead the development of technology solutions to evaluate AI-based systems, ensuring they comply with the EU AI Act. My role encompasses both hands-on development and architectural design, as well as managing a diverse international team, including contractual employees and student assistants. Additionally, I provide expert consultancy in the field of AI system quality assurance.
}
\vspace{0.8ex}
\cventry{November 2023 -- Present}{Lecturer (Part-time)}{HDA}{Darmstadt, Germany}{}{
  As a Lecturer, I engage with first-year Bachelor of Science students, helping them gain foundational knowledge in programming.}
\vspace{0.8ex}
\cventry{January 2020 -- October 2023}{Researcher/ Lecturer}{Technische Universität Darmstadt}{Darmstadt, Germany}{}{
  I specialized in designing and constructing AI-based code models that prioritize reliability, explainability, and a deep understanding of software semantics. My research advanced API misuse detection and program security standards. Additionally, I teach graduate and undergraduate-level courses on programming languages and AI based software assistance, and I am a member of the university's hiring committee (Berufskomission).
}
\vspace{0.8ex}
\cventry{December 2016 -- January 2020}{IT Consultant/Software Architect}{Itemis AG}{Stuttgart, Germany}{}{
  I designed and developed bespoke domain-specific languages and modelling tools, primarily catering to clients in the automotive and embedded systems industries. This involved understanding their unique needs, crafting precise language specifications, and building user-friendly tools to improve their operational efficiency and project effectiveness.
}
\vspace{0.8ex}
\cventry{September 2013 -- December 2016}{Research/Teaching Assistant}{Goethe Universität}{Frankfurt, Germany}{}{Managed the foundations of programming languages lecture series while conducting research on addressing productivity issues associated with software evolution.}
\vspace{0.8ex}
\cventry{September 2011 -- September 2013}{Research/Teaching Assistant}{Universität des Saarlandes}{Saarbrücken, Germany}{}{Contributed to the software engineering chair as a research assistant, supported graduate-level courses on software engineering and security, and aided the team in developing advanced program analysis tools for android malware detection.}
\vspace{0.8ex}
\cventry{September 2010 -- September 2011}{Software Development Engineer}{Scantron}{Chennai, India}{}{Developed and maintained a diverse software suite for the education sector, utilizing languages such as Script\#, SQL, and JavaScript. Collaborated with a team of developers and testers to deliver high-quality software products.}
\vspace{0.5ex}
\section{Education}
\cventry{2014--2017}{Ph.D. in Computer Software}{Goethe Universität}{Frankfurt, Germany}{Suma cum laude}{\raggedright\textbf{Thesis} - \texttt{Combining user interaction and automation to evolve source code.}}
\vspace{0.5ex}
\cventry{2011--2014}{Master of Science - MSc, Computer Science}{Universität des Saarlandes}{Saarbrücken, Germany}{}{\raggedright\textbf{Thesis} - \texttt{Android decompression chamber:A hybrid(static/dynamic) approach to detecting android malware.}}
\vspace{0.5ex}
\cventry{2007--2010}{Master of Computer Applications - MCA}{Anna University}{Chennai, India}{}{}
\cventry{2004--2007}{Bachelor of Science - BSc, Mathematics}{University of Madras}{Chennai, India}{}{}

\section{Service}
I have served on the program committee of several top-tier software engineering conferences including \href{https://2021.ecoop.org/committee/ecoop-2021-ecoop-artifacts-artifact-evaluation-committee}{ECOOP}, \href{https://conf.researchr.org/committee/sle-2019/sle-2019-papers-artifact-evaluation-committee}{SLE}, \href{https://conf.researchr.org/committee/issta-2021/issta-2021-artifact-evaluation-artifact-evaluation-committee}{ISSTA}, and \href{https://2020.splashcon.org/committee/splash-2020-Artifacts-artifact-evaluation-committee}{OOPSLA}.


\section{Projects}
\cvitem{jGuard}{Java extensions that allow making APIs misuse resilient by design (MPS-based). \href{https://youtu.be/tnQGMyMjZRA}{Video demonstration }}
\cvitem{Transparent abstractions}{Effective methods to simplify software reuse - \href{https://fileadmin.cs.lth.se/cs/research/sde/transparent-abstractions/}{Website}}
\cvitem{CogniCrypt}{State of the art in allow-listing based API misuse detection. \href{https://www.eclipse.org/cognicrypt/}{Website}}
\cvitem{mbeddr}{an extensible set of integrated languages for embedded software development - \href{http://www.mbeddr.com}{Website}}

\section{Skills}
\cvitem{Technical skills}{
  Experienced in object oriented programming languages and building domain-specific languages/ modelling tools using XText and Jetbrains MPS. Skilled in static/dynamic program analysis and tooling for code assistance. Experienced in building cloud-based AI solutions on top of Azure. Proficient in software design, maintenance, and security.
}
\cvitem{Soft skills}{
  Experienced in technical writing, presenting, and leadership. Strong collaborator with international and inter-disciplinary teams. Effective educator at graduate and undergraduate level.
}

\section{References}
\begin{enumerate}
  \item \cvitem{Prof. Dr. Christoph Reichenbach}{Relationship: Supervisor, \href[]{https://cs.lth.se/index.php?id=161434}{Homepage}, Contact: creichen@acm.org, christoph.reichenbach@cs.lth.se }
  \item \cvitem{Dr.Julia Lawall}{Relationship: Supervisor, \href[]{https://who.paris.inria.fr/Julia.Lawall/}{Homepage}, Contact: julia.lawall@inria.fr}
  \item \cvitem{Prof. Dr.Rodrigo Bonifacio}{Relationship: International Collaborator, \href[]{https://rbonifacio.github.io/}{Homepage}, Contact: rbonifacio123@gmail.com}
  \item \cvitem{Prof. Dr.Mira Mezini (use only when needed)}{Relationship: Managing Professor, \href[]{https://www.stg.tu-darmstadt.de/main_stg/staff_stg/mira_mezini_1.en.jsp}{Homepage}, Contact: mezini@informatik.tu-darmstadt.de}
\end{enumerate}

\newpage
\input{publications.tex}
\end{document}
